Structure Learning for $\VAR(p)$ Models

### 2019-06-18 paper/paper.tex
Parallel implementation of pairwise GC stats.

In reference to figure \ref{fig:simulation_results} it should not be
overly surprising that our PWGC algorithm performs better than the
LASSO for the case of a strongly causal graph, since in this case the
assumptions which guarantee the correctness of Algorithm
\ref{alg:pwgr_heuristic} hold.  However, the performance is still
markedly superior in the case of a more general DAG.  Finally, we
remark that the PWGC algorithm can be extended to apply to more
general graphs via sequential application.  We will also see in
section \ref{sec:application} that our algorithm can scale effectively
to large problems.

>>>>

In reference to figure \ref{fig:simulation_results} it should not be
overly surprising that our PWGC algorithm performs better than the
LASSO for the case of a strongly causal graph, since in this case the
assumptions which guarantee the correctness of Algorithm
\ref{alg:pwgr_heuristic} hold.  However, the performance is still
markedly superior in the case of a more general DAG.  Finally, we
remark that the PWGC algorithm can be extended to apply to more
general graphs via sequential application.

In regards scalability, we have observed that performing the $O(n^2)$
pairwise Granger-causality calculations consumes the vast majority
($> 90\%$) of the computation time.  Since this step is trivially
parallelizable\footnote{We admit that we are using only a
  single-threaded implementation}, our algorithm should scale well
with multiple cores or multiple machines.

% We will also see in section \ref{sec:application} that our algorithm
% can scale effectively to large problems.
